---
title: "code"
author: "Shahar Chaikin"
date: "2024-10-24"
output: html_document
---
In this code I will provide measures of fish species depth range (1) and depth niche (2) in both the Red Sea and Mediterranean Sea. The overarching goal is to provide a refined information regarding species depths and compare to current knowledge available in FishBase.

Libraries
```{r}
library(tidyverse)
library(rfishbase)
```

#Data
```{r}
#Add invasive state
traits=readxl::read_excel(path = "C:\\Users\\User\\Desktop\\research\\phd\\projects\\invasiveness_red_med\\project_folders\\data\\Belmaker_Species_Traits.xlsx",sheet = 1)
traits$Lessepsian=as.factor(traits$Lessepsian)

data_bruvs=read.csv("C:\\Users\\User\\Desktop\\research\\phd\\projects\\invasiveness_red_med\\project_folders\\data_wrangling_clean_output\\med_red_MaxN_data.csv") %>% 
  left_join(traits %>% select(species=Species_updated_name_fishbase,is_les=Lessepsian),
            by="species") %>% 
  mutate(is_les=case_when(species%in%"Lethrinus borbonicus"~"1",
                          TRUE~is_les))
```

Extract raw depth ranges using BRUVs data per sea
```{r}
bruvs_raw_depth=data_bruvs %>% 
  group_by(sea,species,is_les) %>% 
  summarise(min_depth=min(depth),
            median_depth=median(depth),
            max_depth=max(depth),
            occ=n()) #%>% 
 # filter(occ>1)
```

Extract fishbase depths
```{r}
#Species list to be used
sp_list=data_bruvs %>% 
  distinct(species,is_les) %>% 
  separate_wider_delim(species, delim = " ", names = c("Genus", "Species"),cols_remove = F) %>% 
  left_join(fb_tbl(tbl="species") %>% #Extracting the FishBase SpecCode of the species
              select(SpecCode,Genus,Species),by = c("Genus","Species"))

##Add some code manually for species with NAs
t_grabata=8969
T_erythraeensis="No records"
C_fulvoguttatus=1926
C_dimidiata=11861

sp_list=sp_list %>% 
  mutate(SpecCode=case_when(
    species%in%"Taeniura grabata"~t_grabata,
    #species%in%"Thamnaconus erythraeensis"~T_erythraeensis,
    species%in%"Carangoides fulvoguttatus"~C_fulvoguttatus,
    species%in%"Chromis dimidiata"~C_dimidiata,
    TRUE~SpecCode)) %>% 
  left_join(fb_tbl(tbl="species") %>% #update sp_names by FB
              select(SpecCode,fb_Genus=Genus,fb_Species=Species),
            by = c("SpecCode")) %>% 
  mutate(fb_Genus=case_when(
    Genus%in%"Thamnaconus"~"Thamnaconus",
                            TRUE~fb_Genus),
         fb_Species=case_when(
           Species%in%"erythraeensis"~"erythraeensis",
                            TRUE~fb_Species),
    fb_species_binom=paste(fb_Genus,fb_Species),
    updated_name=(fb_species_binom==species)*-1)


#Update names in bruvs data as well
bruvs_raw_depth=bruvs_raw_depth %>% 
  left_join(sp_list %>%
              select(species,fb_species_binom),
            by="species")
```

#Use the above sp_list to extract depth info from FishBase
```{r}
# fishbase_depths=estimate(species_list = sp_list$fb_species_binom,fields = c("SpecCode","ComDepthMin","ComDepthMax","ComDepMinObserved","ComDepMaxObserved","DepthMin","DepthMax","DepthMinEstimate","DepthMaxEstimate")) %>%
#   left_join(sp_list %>% select(SpecCode,fb_species_binom),
#             by="SpecCode") %>%
#   relocate(last_col())
# write.csv(fishbase_depths,"fishbase_depths.csv",row.names = F)
fishbase_depths=read.csv("fishbase_depths.csv")
```

#Raw depth estimates
Combine raw depths with FishBase information
```{r}
bruvs_raw_vs_fishbase=bruvs_raw_depth %>% 
  left_join(fishbase_depths, by="fb_species_binom") %>% 
  mutate(novel_min_depth=case_when(min_depth<DepthMin~"yes",
                                   TRUE ~"no"),
         novel_max_depth=case_when(max_depth>DepthMax~"yes",
                                   TRUE ~"no"),
         either_min_max=case_when(
      novel_min_depth == "yes" | novel_max_depth == "yes" ~ "yes",
      species%in%"Thamnaconus erythraeensis"~"yes",
      species%in%"Pseudanthias gibbosus"~"yes",
      TRUE ~ "no"),
      max_depth_diff=max_depth-DepthMax,
      min_depth_diff=DepthMin-min_depth,
      rare_record_min=case_when(median_depth<DepthMin~"yes",
                                   TRUE ~"no"),
         rare_record_max=case_when(median_depth>DepthMax~"yes",
                                   TRUE ~"no"),
         rare_either_min_max=case_when(
      rare_record_min == "yes" | rare_record_max == "yes" ~ "yes",
      TRUE ~ "no")) %>% 
  select(-c(DepthMinEstimate,DepthMaxEstimate,ComDepMinObserved,ComDepMaxObserved,species)) %>% 
  relocate(fb_species_binom, .after=sea) %>% 
  mutate(label=case_when(is_les%in%1~"*",
                         TRUE~""))

#How many species have distinct records?
bruvs_raw_vs_fishbase %>% 
  group_by(sea,either_min_max,is_les) %>% 
  summarise(n=n())

#How many species have distinct max depth?
bruvs_raw_vs_fishbase %>% 
  group_by(sea,novel_max_depth) %>% 
  summarise(n=n())

#On average, how much do we add to new maximum depths for species that were found deeper?
bruvs_raw_vs_fishbase %>% 
  filter(novel_max_depth%in%"yes") %>% 
  ungroup() %>% 
  summarise(n=n(),
            mean_new_max_diff=mean(max_depth_diff),
            max_new_max_diff=min(max_depth_diff),
            min_new_max_diff=max(max_depth_diff),
            conf_low=confint(lm(max_depth_diff~1))[1,1],
            conf_high=confint(lm(max_depth_diff~1))[1,2])

#On average, how much do we add to new minimum depths for species that were found shallower?
bruvs_raw_vs_fishbase %>% 
  filter(novel_min_depth%in%"yes") %>% 
  ungroup() %>% 
  summarise(n=n(),
            mean_new_max_diff=mean(min_depth_diff),
            max_new_max_diff=min(min_depth_diff),
            min_new_max_diff=max(min_depth_diff),
            conf_low=confint(lm(min_depth_diff~1))[1,1],
            conf_high=confint(lm(min_depth_diff~1))[1,2])

#How many species deep borders ends beofre 40?
bruvs_raw_vs_fishbase %>% 
  filter(novel_max_depth%in%"yes") %>% 
  group_by(sea,species) %>% 
  summarise(potential_scuba_bias=DepthMax<=40) %>% 
  filter(!species%in%c("Thamnaconus erythraeensis","Pseudanthias gibbosus")) %>% 
  group_by(sea) %>% 
  summarise(n_sp=sum(potential_scuba_bias))

#write.csv(bruvs_raw_vs_fishbase,"depth_range.csv",row.names = F)
```
#habitat
```{r eval=FALSE, include=FALSE}
habitat_fb=rfishbase::ecology(species_list = sp_list$fb_species_binom,
                           server = "fishbase",
                           fields = c("SpecCode","HardBottom","SoftBottom")) %>% 
  left_join(sp_list %>% select(SpecCode,fb_species_binom),
             by="SpecCode") %>%
   relocate(last_col()) %>% 
  mutate(obligator_hard=case_when(HardBottom%in%0 & SoftBottom%in%-1~"yes",
                                  TRUE~"no"),
         obligator_soft=case_when(HardBottom%in%-1 & SoftBottom%in%0~"yes",
                                  TRUE~"no"),
         generalist=case_when(HardBottom%in%0 & SoftBottom%in%0~"yes",
                                  TRUE~"no"))

habitat_bruv=data_bruvs %>% 
  distinct(OpCode,
         sea,
         species) %>% 
  left_join(readxl::read_excel("C:\\Users\\User\\Desktop\\research\\data\\phd_stereo_bruvs\\data\\Metadata.xlsx") %>% 
              select(OpCode,seabed_form)) %>% 
  group_by(species,seabed_form) %>% 
  summarise(occ=n()) %>% 
  spread(key = seabed_form,value = occ,fill = 0) %>% 
  mutate(obligator_hard=case_when(consolidated>0 &
                                    unconsolidated%in%0 &
                                    both%in%0  ~"yes",
                                  TRUE~"no"),
         obligator_soft=case_when(consolidated%in%0 &
                                    unconsolidated>0 &
                                    both%in%0  ~"yes",
                                  TRUE~"no"),
         generalist=case_when(consolidated>0 &
                                    unconsolidated>0 ~"yes",
                                  TRUE~"no")) %>% 
  left_join(sp_list %>%
              select(species,fb_species_binom),
            by="species")
```

Plot it
```{r}
#Mediterranean Sea
med_p=ggplot(bruvs_raw_vs_fishbase %>% 
         filter(either_min_max%in%"yes",
                sea%in%"med"))+
  geom_rect(aes(xmin=30,xmax=40,ymin=0,ymax=12)
            ,alpha=0.05,
            fill="grey")+
  geom_linerange(aes(y=reorder(fb_species_binom,max_depth_diff),
                     xmin=min_depth,
                     xmax=max_depth),
                 color="#55B1DE",
                 size=2.5,
                 alpha=0.75)+
  geom_linerange(aes(y=reorder(fb_species_binom,max_depth_diff),
                     xmin=DepthMin,
                     xmax=DepthMax),
                 color="black",
                 size=1.2)+
  geom_point(data=bruvs_raw_vs_fishbase %>% 
         filter(either_min_max%in%"yes",
                sea%in%"med",
                occ==1),
         aes(x=median_depth,y=fb_species_binom),
                 color="#55B1DE")+
  geom_text(aes(y=fb_species_binom,x=-1.3,label=label),
            vjust=0.8,
            #hjust=-1,
            size=6)+
  labs(title="A) Mediterranean Sea",x="Depth (m)",y="Species")+
  theme_bw()+
  theme(plot.margin = margin(5, 5, 5, 20),  # Left margin wider for long names
        axis.text.y = element_text(face = "italic"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())+
  coord_cartesian(xlim=c(0,160))
med_p
ggsave(plot = med_p, filename = "med_p.png",device ="jpeg",height = 15,width = 10, units = "cm",dpi = 600)

#Red Sea
red_p=ggplot(bruvs_raw_vs_fishbase %>% 
         filter(either_min_max%in%"yes",
                sea%in%"red"))+
  geom_rect(aes(xmin=30,xmax=40,ymin=0,ymax=87)
            ,alpha=0.05,
            fill="grey")+
  geom_linerange(aes(y=reorder(fb_species_binom,max_depth_diff),
                     xmin=min_depth,
                     xmax=max_depth),
                 color="#F74520",
                 size=2.5,
                 alpha=0.75)+
  geom_linerange(aes(y=reorder(fb_species_binom,max_depth_diff),
                     xmin=DepthMin,
                     xmax=DepthMax),
                 color="black",
                 size=1.2)+
  geom_point(data=bruvs_raw_vs_fishbase %>% 
         filter(either_min_max%in%"yes",
                sea%in%"red",
                occ==1),
         aes(x=median_depth,y=fb_species_binom),
                 color="#F74520")+
  geom_text(aes(y=fb_species_binom,x=-1.3,label=label),
            vjust=0.8,
            #hjust=-1,
            size=6)+
  labs(title="B) Red Sea",x="Depth (m)",y="Species")+
  theme_bw()+
  theme(plot.margin = margin(5, 5, 5, 20),  # Left margin wider for long names
        axis.text.y = element_text(face = "italic"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())+
  coord_cartesian(xlim=c(0,160))
red_p
 # ggsave(plot = red_p, filename = "red_p.png",device ="jpeg",height = 30,width = 20, units = "cm",dpi = 600)
```

Combine two plots
```{r}
# Align plot widths
aligned_plots <- cowplot::align_plots(med_p, red_p, align = "v")
both_seas_raw_p=gridExtra::grid.arrange(
  grobs = aligned_plots,
  ncol = 1,
  layout_matrix = rbind(c(1),
                                                       c(2),
                                                       c(2),
                                                       c(2),
                                                       c(2),
                                                       c(2)),
  left = "Species",
  bottom = "Depth (m)"
)

# ggsave(plot = both_seas_raw_p, filename = "both_seas_raw_p.png",device ="jpeg",height = 30,width = 20, units = "cm",dpi = 600)
```

#Central depth niches
##Get the raw data prepared for modelling with zeros
```{r}
#Mediterranean Sea
data_bruvs_with_zeros_med=data_bruvs %>% 
  filter(sea%in%"med") %>% 
  left_join(sp_list %>%
              select(species,fb_species_binom),
            by="species") %>% 
  select(OpCode,
         species=fb_species_binom,
         MaxN) %>% 
  spread(key = species,
         value = MaxN,
         fill = 0) %>% 
  gather(key = species,value = MaxN,2:ncol(.)) %>% 
  left_join(data_bruvs %>% 
              distinct(OpCode,sea,depth),
            by="OpCode")
#Red Sea
data_bruvs_with_zeros_red=data_bruvs %>% 
  filter(sea%in%"red") %>% 
  left_join(sp_list %>%
              select(species,fb_species_binom),
            by="species") %>% 
  select(OpCode,
         species=fb_species_binom,
         MaxN) %>%
  spread(key = species,
         value = MaxN,
         fill = 0) %>% 
  gather(key = species,value = MaxN,2:ncol(.)) %>% 
  left_join(data_bruvs %>% 
              distinct(OpCode,sea,depth),
            by="OpCode")
```

#eHOF models
##All species - HOF
###Med
```{r include=FALSE}
ehof_med_all=list()
for (i in data_bruvs_with_zeros_med$species %>% unique){
  
ehof_med_all[[i]]=HOF(
   family=poisson,
   grad=data_bruvs_with_zeros_med %>%
     filter(species%in%i) %>% 
     select(depth) %>% pull(),
   occ=data_bruvs_with_zeros_med %>% 
     filter(species%in%i) %>%
     select(MaxN) %>% 
     pull(),
   M=data_bruvs_with_zeros_med %>%
     filter(species%in%i) %>%
     summarise(max=max(MaxN)) %>%
     pull(),
   modeltypes=c("I","II","III","IV","V"))
}
ehof_med_all
write_rds(ehof_med_all,"HOF_med_all.rds")
```

###Red
```{r include=FALSE}
ehof_red_all=list()
for (i in data_bruvs_with_zeros_red$species %>% unique){
  
ehof_red_all[[i]]=HOF(
   family=poisson,
   grad=data_bruvs_with_zeros_red %>%
     filter(species%in%i) %>% 
     select(depth) %>% pull(),
   occ=data_bruvs_with_zeros_red %>% 
     filter(species%in%i) %>%
     select(MaxN) %>% 
     pull(),
   M=data_bruvs_with_zeros_red %>%
     filter(species%in%i) %>%
     summarise(max=max(MaxN)) %>%
     pull(),
   modeltypes=c("I","II","III","IV","V"))
}
ehof_red_all
write_rds(ehof_red_all,"HOF_red_all.rds")
```

Load HOF outputs
```{r}
HOF_med_all=read_rds("HOF_med_all.rds")
HOF_red_all=read_rds("HOF_red_all.rds")
```

Plot species
```{r}
sp_to_plot_med=bruvs_raw_vs_fishbase %>% 
  ungroup() %>% 
  filter(occ>3,
         sea%in%"med") %>% 
  select(species) %>% 
  pull()

sp_to_plot_red=bruvs_raw_vs_fishbase %>% 
  ungroup() %>% 
  filter(occ>3,
         sea%in%"red") %>% 
  select(species) %>% 
  pull()
```

Loop through all
Med. Sea plots
```{r}
# Create the output folder if it doesn't exist
output_folder <- "species_plots_med"
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Loop through the species list and generate/export plots
for (species_name in sp_to_plot_med) {
  if (species_name %in% names(HOF_med_all)) {
    plot_data <- HOF_med_all[[species_name]]
    plot_filename <- file.path(output_folder, paste0(gsub(" ", "_", species_name), ".png"))

    # Open a PNG device with specified resolution
    png(filename = plot_filename, width = 1200, height = 800, res = 300)
# Adjust plot margins using par()
    par(mar = c(3, 3.5, 1, 3.5) + 0.1, # bottom, left, top, right margins
        mgp = c(2, 0.8, 0),# Title on position 2, labels on 0.8, axis line on 0
     # Control text sizes
      cex.axis = .5,
      cex.lab = .5,
      cex.main = 1,
      cex.legend = .7)
    
    # Create the plot
    plot(plot_data, boxp = FALSE, main = species_name,
         xlab = "Depth (m)", ylab = "Expected MaxN",para = F) # Add meaningful labels

    # Close the PNG device to save the plot
    dev.off()

    cat(paste("Plot for", species_name, "exported to:", plot_filename, "\n"))
  } else {
    cat(paste("Warning: No data found for species:", species_name, "\n"))
  }
}

cat("All plots exported successfully to the '", output_folder, "' folder.\n", sep = "")
```

Expord Red Sea plots
Red Sea plots
```{r}
# Create the output folder if it doesn't exist
output_folder <- "species_plots_red"
if (!dir.exists(output_folder)) {
  dir.create(output_folder)
}

# Loop through the species list and generate/export plots
for (species_name in sp_to_plot_red) {
  if (species_name %in% names(HOF_red_all)) {
    plot_data <- HOF_red_all[[species_name]]
    plot_filename <- file.path(output_folder, paste0(gsub(" ", "_", species_name), ".png"))

    # Open a PNG device with specified resolution
    png(filename = plot_filename, width = 1200, height = 800, res = 300)
# Adjust plot margins using par()
    par(mar = c(3, 3.5, 1, 3.5) + 0.1, # bottom, left, top, right margins
        mgp = c(2, 0.8, 0),# Title on position 2, labels on 0.8, axis line on 0
     # Control text sizes
      cex.axis = .5,
      cex.lab = .5,
      cex.main = 1,
      cex.legend = .7)
    # Create the plot
    plot(plot_data, boxp = FALSE, main = species_name,
         xlab = "Depth (m)", ylab = "Expected MaxN") # Add meaningful labels

    # Close the PNG device to save the plot
    dev.off()

    cat(paste("Plot for", species_name, "exported to:", plot_filename, "\n"))
  } else {
    cat(paste("Warning: No data found for species:", species_name, "\n"))
  }
}

cat("All plots exported successfully to the '", output_folder, "' folder.\n", sep = "")
```

##All species - Para
###Med
```{r eval=FALSE, include=FALSE}
ehof_med_all_para=list()
for (i in data_bruvs_with_zeros_med$species %>% unique){
  
ehof_med_all_para[[i]]=Para(HOF(
   family=poisson,
   grad=data_bruvs_with_zeros_med %>%
     filter(species%in%i) %>% 
     select(depth) %>% pull(),
   occ=data_bruvs_with_zeros_med %>% 
     filter(species%in%i) %>%
     select(MaxN) %>% 
     pull(),
   M=data_bruvs_with_zeros_med %>%
     filter(species%in%i) %>%
     summarise(max=max(MaxN)) %>%
     pull(),
   modeltypes=c("I","II","III","IV","V")))
}
ehof_med_all_para
write_rds(ehof_med_all_para,"ehof_med_all_para.rds")
```

Transform to df
```{r}
central_borders_med_df <- map_df(names(ehof_med_all_para), ~ {
  species_data <- ehof_med_all_para[[.x]]
  
  # Extract model name
  model_name <- ifelse(is.null(species_data$model), 
                 NA, 
                 species_data$model)
  
  # Extract central border information
  if(!is.null(species_data$centralBorder)) {
    if(length(species_data$centralBorder) == 2) {
      # If centralBorder has lower and upper values
      tibble(
        species = .x,
        model = model_name,
        centralBorder_lower = species_data$centralBorder[1],
        optimum=species_data$opt,
        centralBorder_upper = species_data$centralBorder[2]
      )
    } else {
      # If centralBorder is a single value
      tibble(
        species = .x,
        model = model_name,
        centralBorder = species_data$centralBorder
      )
    }
  } else {
    # If centralBorder is missing
    tibble(
      species = .x,
      model = model_name,
      centralBorder = NA_real_
    )
  }
})

central_borders_med_df =central_borders_med_df %>% 
  left_join(data_bruvs_with_zeros_med %>% 
              group_by(species) %>%
              filter(MaxN>0) %>% 
              summarise(occ=n()),
            by="species") %>% 
  left_join(bruvs_raw_vs_fishbase %>% 
              filter(sea%in%"med") %>% 
              select(species,fb_species_binom),
            by="species") %>% 
  select(-species) %>% 
  relocate(fb_species_binom, .before=model)

# write.csv(central_borders_med_df,"central_borders_med_df.csv",row.names = F)
```

###Red - Para
```{r eval=FALSE, include=FALSE}
ehof_red_all_para=list()
for (i in data_bruvs_with_zeros_red$species %>% unique){
  
ehof_red_all_para[[i]]=Para(HOF(
   family=poisson,
   grad=data_bruvs_with_zeros_red %>%
     filter(species%in%i) %>% 
     select(depth) %>% pull(),
   occ=data_bruvs_with_zeros_red %>% 
     filter(species%in%i) %>%
     select(MaxN) %>% 
     pull(),
   M=data_bruvs_with_zeros_red %>%
     filter(species%in%i) %>%
     summarise(max=max(MaxN)) %>%
     pull(),
   modeltypes=c("I","II","III","IV","V")))
}
ehof_red_all_para
write_rds(ehof_red_all_para,"ehof_red_all_para.rds")
```

Transform to df
```{r}
central_borders_red_df <- map_df(names(ehof_red_all_para), ~ {
  species_data <- ehof_red_all_para[[.x]]
  
  # Extract model name
  model_name <- ifelse(is.null(species_data$model), 
                 NA, 
                 species_data$model)
  
  # Extract central border information
  if(!is.null(species_data$centralBorder)) {
    if(length(species_data$centralBorder) == 2) {
      # If centralBorder has lower and upper values
      tibble(
        species = .x,
        model = model_name,
        centralBorder_lower = species_data$centralBorder[1],
        optimum=species_data$opt,
        centralBorder_upper = species_data$centralBorder[2]
      )
    } else {
      # If centralBorder is a single value
      tibble(
        species = .x,
        model = model_name,
        centralBorder = species_data$centralBorder
      )
    }
  } else {
    # If centralBorder is missing
    tibble(
      species = .x,
      model = model_name,
      centralBorder = NA_real_
    )
  }
})

central_borders_red_df =central_borders_red_df %>% 
  left_join(data_bruvs_with_zeros_red %>% 
              group_by(species) %>%
              filter(MaxN>0) %>% 
              summarise(occ=n()),
            by="species") %>% 
  left_join(bruvs_raw_vs_fishbase %>% 
              filter(sea%in%"red") %>% 
              select(species,fb_species_binom),
            by="species") %>% 
  select(-species) %>% 
  relocate(fb_species_binom, .before=model)

# write.csv(central_borders_red_df,"central_borders_red_df.csv",row.names = F)
```

Bind DFs
```{r}
central_borders_df=bind_rows(central_borders_med_df,
                             central_borders_red_df) %>% 
  rename(species=fb_species_binom) %>% 
  mutate(opt_type=case_when(model%in%"I"~"No optimum",
                            model%in%"II"~"Single point",
                            model%in%"III"~"Depth section",
                            model%in%"IV"~"Single point",
                            model%in%"V"~"Single point")) %>% 
  drop_na(species)
#write.csv(central_borders_df,"central_borders_df.csv",row.names = F)
```

#ggplot example species
```{r}
#Model I
G_j=tibble(
  x=ehof_red_all$`Gymnothorax johnsoni`$x,
  fitted=fitted(ehof_red_all$`Gymnothorax johnsoni`,model = "I"),
  y=ehof_red_all$`Gymnothorax johnsoni`$y
)
G_j_p=ggplot(G_j)+
  geom_point(aes(x=x,y=y),
             color="grey",
             size=1)+
  geom_line(aes(x=x,y=fitted),
            color="black",
            size=1,
            linejoin="round",
            lineend="round")+
  labs(x="Depth (m)",
       y="Expected MaxN",
       title=expression(paste("Model I - ", italic("Gymnothorax johnsoni"))))+
  theme_classic()+
  scale_y_continuous(breaks = seq(0,2,by=1))

#Mpdel II - Thallasoma pavo
T_p=tibble(
  x=ehof_med_all$`Thalassoma pavo`$x,
  fitted=fitted(ehof_med_all$`Thalassoma pavo`,model = "II"),
  y=ehof_med_all$`Thalassoma pavo`$y
)
T_p_p=ggplot(T_p)+
  geom_point(aes(x=x,y=y),
             color="grey",
             size=1)+
  geom_line(aes(x=x,y=fitted),
            color="red",
            size=1,
            linejoin="round",
            lineend="round")+
  labs(x="Depth (m)",
       y="Expected MaxN",
       title=expression(paste("Model II - ", italic("Thalassoma pavo"))))+
  theme_classic()+
  scale_y_continuous(breaks = seq(0,2,by=1))
#Model III - Pagrus caeruleostictus
P_c=tibble(
  x=as.numeric(seq(0,150,by=1)),
  predicted=as.numeric(predict(ehof_med_all$`Pagrus caeruleostictus`,model = "III",newdata = data.frame(x = 0:150))[,])
)
P_c_p=ggplot(P_c)+
  # geom_point(aes(x=x,y=y),
  #            color="grey",
  #            size=1)+
  geom_line(aes(x=x,y=predicted),
            color="green",
            size=1,
            linejoin="round",
            lineend="round")+
  labs(x="Depth (m)",
       y="Expected MaxN",
       title=expression(paste("Model III - ", italic("Pagrus caeruleostictus"))))+
  theme_classic()#+
  #scale_y_continuous(breaks = seq(0,1,by=.25))
P_c_p
#Model IV - 

#Model V - 
```


